Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Add navigation application with reference

Description of the field of city reproduction (Parish Müller).

@@

@@

% Thursday:
% TODO: Fix citings like they appear in the example thesis
% TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture

>>>>

Description of the field of city reproduction (Parish Müller, procedural modeling of ciites).

@@

Applications:
    Navigating agents or pedestrian flows.
    Using a road network to creates an underlying navmesh
    This process is analytical and relies on the availablity and accurate representation of city maps.
    %TODO: (Parish Müller: Procedural modelin of cities)

@@

% Thursday:
% TODO: Fix citings like they appear in the example thesis
% TODO: Collision study implementation, disposition
    % TODO: Figure detailing the steps in the point-matching algorithm
    % TODO: Edge distance algorithm, outline, algorithm + picture
% TODO: Introduction references
% TODO: Write introduction
